Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-03-07 doc/JFM2022/reviews/ResponseToReviewer3.tex

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Professor Petia Vlahovska,
\\ \\
\noindent
We thank you for handling the manuscript and the Reviewers for carefully
evaluating our work. The revisions address all the comments and
concerns raised by the Reviewers and we believe the result is a
significantly improved manuscript. An itemized list of the specific
changes and responses follows. Changes to the manuscript from Reviewers
1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 3}
\comment{\noindent
The manuscript extends the authors’ previous work on modeling
amphiphilic particles in a viscous solvent to modeling amphiphilic Janus
particles suspended in a viscous background flow. The authors adopted
the GMRES iterative method to solve the screened Laplace equation for
hydrophobic attraction. They investigated the inter-monolayer friction
of vesicles formed by amphiphilic Janus particles and corresponding
membrane ruptures in viscous flows, and simulated the spatial migration
dynamics of a vesicle in a parabolic flow and also the hydrodynamics of
two vesicles in shear and extensional flows.
\\ \\
\noindent
This manuscript presents a systematic study of the hydrodynamics of
vesicles formed by amphiphilic Janus particles in viscous flows. It
provides quantitative analysis of the inter-monolayer friction, membrane
permeability and the migration dynamics of soft suspended vesicles. The
topic on hydrodynamics of complex fluids is interesting, and this
research fits the scope of Journal of Fluid Mechanics. Here, I am in a
favor of its publication at some points if the authors can address the
following concerns in the revised manuscript.
}
\begin{itemize}
\item We thank the Reviewer for their positive feedback
  and suggestions which have helped improve the content and presentation
    of the manuscript.
\end{itemize}

@@

This is evidence that the lubrication hydrodynamics of the thin film between two particles under the repulsive Morse potential is well captured if the flow velocity can be accurately calculated in the boundary integral simulations when two particles are sufficiently close to each other and the short-range repulsion is the dominant force.

In this work we used similar numerical techniques to solve the integral equations when some boundaries are quite close to each other. As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.

\item Change: We added added a paragraph at the end of Section 2.2
  describing how the lubrication hydrodynamics in a narrow space between
    boundaries is well-captured within the boundary integral
    formulation. Then, in section 4.1 \textit{Model Parameters}, we
    show quantitatively how the lubrication and artificial repulsion are
    comparable when substituting for our simulation parameters.
\end{itemize}

@@

\noindent
\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
\item Response: We thank the Reviewer for highlighting this qualitative aspect of
  the curves.

\item Change: We modified the second to last paragraph in Section 4.2.1,
 noting that the frequencies correspond to the tank-treading of the slightly
  polygonal vesicle and individual particles, respectively. 
  Moreover, we scaled the abscissas of Figure 3 to percent, and corrected
  an erroneous scale factor in the time axes. 
\end{itemize}

\noindent
\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
\item Response: Fig.~6 shows 4 snapshots in the time frame from 0 to 12
  $\mu$s along with the trajectory of the centroid.

@@

  \item Change: In the caption of Fig.~6, we now clarify that the
    horizontal axis represents time and that the vertical axis has been
    scaled to make the migration stand out.

\end{itemize}

\noindent
\comment{{\bf 4.} In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
\item Response: We thank the Reviewer for pointing this out.
  This issue occurred due to a limitation of the software used
  to generate streamlines in post-processing.

\item Change: We improved the software and the corrected streamlines now appear in Fig.~11.
  As expected, the streamlines are continuous while their gradient is
    piecewise continuous
  across the JP vesicle interface.
\end{itemize}

\noindent
\comment{Minor: I read some grammatical errors in the manuscript that
should be corrected, i.e., ``replicate well-know vesicle hydrodynamics
$\ldots$" on page 2, ``$\ldots$ a baseline JP vesicles $\ldots$" on page
8, ``circular vesicles has a Laplace pressure $\ldots$" at Eq.~(4.7).
The authors are suggested to have a thorough read of the manuscript.}
\begin{itemize}
  \item The typo with ``well-know" is corrected, but colored in
    \textcolor{red}{red} since it was pointed out by Reviewer 1 as well.

@@

  \item The manuscript now reads
    \begin{quotation}
      $\ldots$ a baseline JP vesicle $\ldots$
    \end{quotation}

  \item The typo with ``has" instead of ``have" is corrected, but
    colored in \textcolor{red}{red} since it was pointed out by Reviewer
    1.

### 2022-03-07 doc/JFM2022/main_jfm.tex
fixing directory structure so that we can publish more than one paper

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles
\ReviewerTwo{and empitically deduced realistic bending moduli, stretching moduli,
  and tilt moduli under reasonable assumptions for the input parameters.}
In the present work, we study JP vesicles in various background flows.
We also perform parametric studies of effective properties of the JP vesicles 
as a function of particle size and interaction strength.

@@

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water. 
\ReviewerThree{
  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
  prevents particle collisions and is comparable to hydrodynamic lubrication.
  \citep{cawthorn_balmforth_2010} provide the asymptotic expression 
  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
  because the particle gaps are comparable to the particle radius
  and the relative velocities $\dot \epsilon$ between particles are on
  the order of a nm $\text{ns}^{-1}$.
}

To reach consistent simulation outcomes, we first solve for a baseline
JP \ReviewerThree{vesicle} that is suitably close to equilibrium. We
start with an assumed configuration of $N=58$ JP in the form of two,
circular, apposing monolayers of about $8$ nm in radius. The norms of
the translational and rotational velocities vanish exponentially with an
approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium
configuration is therefore rapidly attained. This equilibrium
configuration serves as the initial data in the subsequent background
flow simulations.

@@

Figure~\ref{figure3} shows snapshots of the JP vesicle in the shear flow
with $\chi=0.0025$. Under the background flow, the rigid-body boundary
condition~\eqref{eq:rigid_bc} causes the particle suspension to
elongate. This perturbation disrupts the preferred particle orientations
and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
red region). In response, hydrophobic
attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
reorient and form a somewhat elliptically-shaped suspension. Panel (a)
shows the initial configuration and panel (b) shows the later,
fully-formed, clockwise tank-treading motion. The JP suspension
maintains its bilayer structure throughout the simulation. 
%

@@

Figure~\ref{figure5}a illustrates inter-monolayer slip by tracking the distances
traveled by a pair of particles along the midplane curve. In the left image, the blue and yellow
particle lie next to each other. In the right-most panel, the yellow
particle has traveled farther than the blue particle. This suggests that
the outer tangential velocity, obtained by projecting the velocity of the
outer leaflet onto the midplane curve, 
is larger than that of the inner leaflet.

@@

We show snapshots of the fluid pressure in Figure~\ref{figure10}. Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{0.5,1,1.5\}$ $\upmu$s, and the
streamlines are plotted in the background for all panels. 
We include the numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.
We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
attraction (Figure~\ref{figure10}c). Similar dynamics have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behaviour is absent when two JP vesicles are well-separated.

@@

Using a similar setup to the shear flow case, we suspend the same two,
pre-relaxed, $58$-body JP vesicles and consider their dynamics in an
extensional flow 
\begin{equation}
\uu_{\infty}(\xx) = \dot \gamma ((\mathbf{e}_x \cdot \xx)\mathbf{e}_x - (\mathbf{e}_y \cdot \xx)\mathbf{e}_y)
\end{equation}
with extensional rate $\dot \gamma =0.005$ ns$^{-1}$. This extensional
flow is stretching in the $y$-direction and squeezing in the
$x$-direction. Figure~\ref{figure11} shows how the initial placement of
the JP vesicles affects the dynamics. When two centroids are both placed
symmetrically on the $x$-axis (case (i)), the JP vesicles come into
contact and reach a steady equilibrium. If one centroid is placed above
the $x$-axis (case (ii)), the two JP vesicle move together and then
upward. The migration of the right JP vesicle is a consequence of the
adhesive effect caused by the hydrophobic interactions. When the two
centroids start on opposite sides of the $x$-axis (case (iii)), they
eventually diverge from one another along the $\pm y$-directions.
Finally, when the two centroids start on opposite sides of the $x$-axis,
but with a greater displacement (case (iv)), the JP vesicles move much
faster along the $\pm y$-directions.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model
    for two vesicles in shear flow and in extensional flow.
  The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
  the proposed HAP model.}
\end{figure}

\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
insets in Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows 
trajectory comparisons between the proposed model and the continuum modeling for both 
shear flow and extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$
represents the distance between two centroids of JP vesicles. The centroid positions are 
identical for both models and the geometry in the continuum model is created along the 
midplane locations of JP vesicles and the initial reduced area is matched. Panel (a) shows that 
the results of continuum model does not have a periodic motion and two vesicles flow apart 
after 1.5 $\mu$s. Panel (b) shows that the results of continuum model has similar trend of
dynamics with one in the proposed model.}

>>>>

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles
\ReviewerTwo{and empirically deduced realistic bending moduli, stretching moduli,
  and tilt moduli under reasonable assumptions for the input parameters.}
In the present work, we study JP vesicles in various background flows.
We also perform parametric studies of effective properties of the JP vesicles 
as a function of particle size and interaction strength.

@@

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water. 
\ReviewerThree{
  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
  prevents particle collisions and is comparable to hydrodynamic lubrication.
  With a slight modification, the appendix of
  \citep{cawthorn_balmforth_2010} provides the asymptotic expression 
  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
  because the particle gaps are comparable to the particle radius
  and the relative velocities $\dot \epsilon$ between particles are on
  the order of a nm $\text{ns}^{-1}$.
}

To reach consistent simulation outcomes, we first solve for a baseline
JP \ReviewerThree{vesicle} that is suitably close to equilibrium. We
start with an assumed configuration of $N=58$ JP in the form of two,
circular, apposing monolayers of about $8$ nm in radius. The norms of
the translational and rotational velocities vanish exponentially with an
approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium
configuration is therefore rapidly attained, as illustrated by Supplementary Movie S1. 
This equilibrium
configuration serves as the initial data in the subsequent background
flow simulations.

@@

Figure~\ref{figure3} shows snapshots of the JP vesicle in the shear flow
with $\chi=0.0025$. Under the background flow, the rigid-body boundary
condition~\eqref{eq:rigid_bc} causes the particle suspension to
elongate. This perturbation disrupts the preferred particle orientations
and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
red region). In response, hydrophobic
attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
reorient and form a somewhat elliptically-shaped suspension. Panel (a)
shows the initial configuration and panel (b) shows the later,
fully-formed, clockwise tank-treading motion. The JP suspension
maintains its bilayer structure throughout the simulation. 
(See Supplementary Movie S2 for tank-treading vesicle with $\chi=0.005$.)
%

@@

Figure~\ref{figure5}a illustrates inter-monolayer slip by tracking the distances
traveled by a pair of particles along the midplane curve. In the left image, the blue and yellow
particle lie next to each other. In the right-most panel, the yellow
particle has traveled farther than the blue particle. This suggests that
the outer tangential velocity, obtained by projecting the velocity of the
outer leaflet onto the midplane curve, 
is larger than that of the inner leaflet 
(see Supplementary Movie S3).

@@

We show snapshots of the fluid pressure in Figure~\ref{figure10}. 
Supplementary Movie S5 shows the overall vesicle interaction.
Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{0.5,1,1.5\}$ $\upmu$s, and the
streamlines are plotted in the background for all panels. 
We include the numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.
We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
attraction (Figure~\ref{figure10}c). Similar dynamics have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behaviour is absent when two JP vesicles are well-separated.

@@

Using a similar setup to the shear flow case, we suspend the same two,
pre-relaxed, $58$-body JP vesicles and consider their dynamics in an
extensional flow 
\begin{equation}
\uu_{\infty}(\xx) = \dot \gamma ((\mathbf{e}_x \cdot \xx)\mathbf{e}_x - (\mathbf{e}_y \cdot \xx)\mathbf{e}_y)
\end{equation}
with extensional rate $\dot \gamma =0.005$ ns$^{-1}$. This extensional
flow is stretching in the $y$-direction and squeezing in the
$x$-direction. Figure~\ref{figure11} shows how the initial placement of
the JP vesicles affects the dynamics. When two centroids are both placed
symmetrically on the $x$-axis (case (i)), the JP vesicles come into
contact and reach a steady equilibrium. If one centroid is placed above
the $x$-axis (case (ii)), the two JP vesicle move together and then
upward. The migration of the right JP vesicle is a consequence of the
adhesive effect caused by the hydrophobic interactions. When the two
centroids start on opposite sides of the $x$-axis (case (iii)), they
eventually diverge from one another along the $\pm y$-directions.
Finally, when the two centroids start on opposite sides of the $x$-axis,
but with a greater displacement (case (iv)), the JP vesicles move much
faster along the $\pm y$-directions (see Supplementary Movie S6).

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model
    for two vesicles in shear flow and in extensional flow.
  The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thin curves plot the trajectories
  of $d_{1,2}$ generated by the continuum model and the thick curves are computed from using
  the proposed HAP model.}
\end{figure}

\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
insets in Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows 
trajectory comparisons between the proposed model and the continuum modeling for both 
shear flow and extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$
represents the distance between two centroids of JP vesicles. The centroid positions are 
identical for both models and the geometry in the continuum model is created along the 
midplane locations of JP vesicles and the initial reduced area is matched. Panel (a) shows that 
the results of continuum model does not have a periodic motion and two vesicles flow apart 
after 1.5 $\mu$s. Panel (b) shows that the results of the continuum model have a similar trend as  the proposed model.}
